Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-18 paper.tex
some restructuring
start of toil

        \subsection{limitations of SPM}
    \section{Nextflow}
        \subsection{summary}
        Nextflow is a POSIX-compatible pipeline engine for scientific workflows.
It extends the Groovy programming language to provide an  intuitive domain-specific language (DSL) 
that enables users to easily describe their workflows. Unlike pipeline engines such as Nipype and
PSOM, Netflow does not employ DAG. It instead adheres to the
\textit{Dataflow} programming model which decides how data will flow through the pipeline at
runtime \note{fix this sentence}. Nextflow prides itself on allowing the
integration of containerized tools to address the issue of numerical instability
that may arise from different environment setups.

@@

    \section{Geneflow}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Toil}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Thunder}

>>>>

        \subsection{limitations of SPM}

@@

        \section{Nextflow}
        \subsection{summary}
        Nextflow is a POSIX-compatible pipeline engine for scientific workflows.
It extends the Groovy programming language to provide an  intuitive domain-specific language (DSL) 
that enables users to easily describe their workflows. Unlike pipeline engines such as Nipype and
PSOM, Netflow does not employ DAG. It instead adheres to the
\textit{Dataflow} programming model which decides how data will flow through the pipeline at
runtime \note{fix this sentence}. Nextflow prides itself on allowing the
integration of containerized tools to address the issue of numerical instability
that may arise from different environment setups.

    \section{Geneflow}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Toil}
        Toil is another general workflow framework aimed at the processing of scientific big data, with its main focus being on
        genomics workflows. It prides itself in not only its ability to not only scale the processing of very large datasets,
        but also its portability, allowing it to be executed on any environment. Toil pipelines can be written in CWL, WDL (Workflow Description Language) and Python,
        with its Python API permitting the dynamic declaration of workflows. The Toil workflow framework is also open-sourced, making it a community-driven effort \note{as is the case with most}
        \subsection{Pipeline description}

        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Thunder}
